%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://aeilot.top/}{\Large Chenluo Deng}} & Email: \href{mailto:louisaeilotd@gmail.com}{louisaeilotd@gmail.com}\\
  \href{https://aeilot.top/}{aeilot.top} \textbar\ LinkedIn: \href{https://www.linkedin.com/in/chenluo-d-85b37a33a/}{chenluo-d-85b37a33a} & Mobile: \href{tel:+8618021050987}{+86-180-2105-0987} \\
\end{tabular*}

\section{Objective}
{AI/ML-focused engineering student seeking internships in machine learning engineering; passionate about machine learning systems; experienced in synthetic data generation and software development.}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {School of Artificial Intelligence, Shanghai Jiao Tong University}{Shanghai, China}
      {Bachelor of Engineering}{2025 -- 2029 (Expected)}
      \resumeItemListStart
        \resumeItem{Key Coursework}
          {Data Structures \& Algorithms; Linear Algebra; Self-learning Operating Systems, Computer Vision, and Deep Learning}
      \resumeItemListEnd
    \resumeSubheading
      {No.2 High School of East China Normal University}{Shanghai, China}
      {High School Diploma; Graduated with Distinction ($<3\%$)}{Sep 2022 -- Jun 2025}

  \resumeSubHeadingListEnd

%-----------Experience-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Open Source}{2020 -- present}
      {48 public repositories on GitHub: \href{https://github.com/aeilot}{https://github.com/aeilot}}{Online}

    \resumeSubheading
      {Technicians of the Students’ Association Union}{2022 -- 2025}
      {No.2 High School of East China Normal University}{On-site}
      \resumeItemListStart
        \resumeItem{HSEFZ Digital Life}
              {A unified portal integrating seven major campus services (e.g., volunteer hour tracking, club yearbook, sports leagues) developed with Django.}
      \resumeItemListEnd

    \resumeSubheading
      {Deputy Programming Group Lead at Zodiac 6353}{2022 -- 2024}
      {No.2 High School of East China Normal University}{On-site}
      \resumeItemListStart
        \resumeItem{FIRST Robotics Competiton}
              {Developed automation for the bot at 2024 Finger Lakes Regional. Taught Java OOP and Git Project Management courses to team members. Contributed to robot assembly and programming.}
      \resumeItemListEnd

    \resumeSubheading
      {Student Researcher of Yingcai Jihua}{2023}
      {Shanghai Jiao Tong University}{Hybrid}
      \resumeItemListStart
        \resumeItem{DeepDarts+}
              {Tutored by Prof. Yong Yu \& his student Lingyue Fu at SJTU Apex Lab, I delved into the prosepct of training deep learning models with computer-generated data through my research project: A Mobile Dart Scoring System Based On Deep-learning Object Detection.Based on DeepDarts developed by scholars at the Unversity of Waterloo, I designed a data generator with OpenSceneGraph and 3D models generated with photogrammetry, demonstrating feasibility and eﬀective‑ness of training models with computer‑generated data.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technicians Lead, Students’ Association Union}{2022 -- 2025}
      {Supported campus services and internal tooling; collaborated with cross-functional student teams}{On-site}

    \resumeSubheading
      {Deputy Programming Group Lead, Zodiac 6353 (FRC)}{2022 -- 2024}
      {Led training and code reviews; delivered workshops on Java OOP and Git-based project management; served as the team coach at the 2024 Finger Lakes Regional}{On-site}
  \resumeSubHeadingListEnd


%-----------Honor-----------------
\section{Honor}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SJTU Zhiyuan Scholarship}{Shanghai, China}
      {Merit-based Scholarship}{2025}

    \resumeSubheading
      {SJTU School of AI 2025 Freshman Hackathon}{Shanghai, China}
      {Second Prize}{2025}

    \resumeSubheading
      {Junyuan Tang Scholarship}{Shanghai, China}
      {Merit-based Scholarship for top 10 students academically}{2024}


    \resumeSubheading
      {The International Forum for Scientific Youth “Step into the Future”}{Moscow, Russia}
      {1st Degree MIREA special diploma \& 3rd Degree Formal Sciences}{2024}

    \resumeSubheading
      {The Program for Talented Youth in STEM or Yingcai Jihua}{Tianjin, China}
      {National Outstanding Qualification in Computer Science}{2023}    
      
    \resumeSubheading
      {National Olympiad in Informatics in Provinces}{Shanghai, China}
      {First Prize}{2022}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Stay Away From My Screen (2026)}
      {An instant digital ``Do Not Touch'' sign for your Mac that prevents fingerprints and protects your display with a single keystroke.}
    \resumeSubItem{JAgenda (2025)}
      {A Hackathon project. An AI (DeepSeek V3.1) agent for time management built with Django.}
    \resumeSubItem{Habits (2025)}
      {A macOS \& iOS Habit Tracker featuring menu bar quick access, with Habits Agent coming soon.}
    \resumeSubItem{DeepDarts+ (2023 -- 2024)}
      {Enhanced an automatic dart scoring system based on YOLOv4 object detection; built a 3D rendering data generator to create 20{,}000 synthetic images in under an hour for retraining and domain adaptation to a custom dartboard; improved side-angle performance by 29\% over the original unaugmented model; shipped an Android app for real-time deployment.}
    \resumeSubItem{HSEFZ Digital Life (2022 -- now)}
      {A unified portal integrating seven major campus services (e.g., volunteer hour tracking, club yearbook, sports leagues) developed with Django.}
    \resumeSubItem{GitHub Dark Mode Safari (2020)}
      {A Safari browser extension adding the Dark Mode feature to GitHub.com.}
    \resumeSubItem{Daily Notes (2019 -- 2021)}
      {A Markdown Note Application written for Android featuring WYSIWYG.}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}
      {C/C++, Java, Python, Swift}
    \resumeSubItem{Frameworks \& Libraries}
      {Django, SwiftUI, Android, PyTorch}
    \resumeSubItem{Databases \& Tools}
      {Linux, uWSGI, Git, GitHub, MySQL, Docker}
  \resumeSubItem{English Language}
      {TOEFL 114 (July 2024) \& SAT 1560 (Aug 2024)}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
